Supplementary material

### 2024-02-05 writing/supplement.Rmd
update post revision title and authors full names

---
title: "Supplementary material"
subtitle: "Main paper: Episodic memory bolsters acquisition of new semantic knowledge in trivia experts"
author: "MT, LW, & MA"
date: "Updated `r Sys.Date()`"
output:
  pdf_document:
    toc: true
  html_document: default
---

>>>>

---
title: "Supplementary material"
subtitle: "Main paper: New semantic knowledge is more strongly coupled with episodic memory in trivia experts"
author: "Monica K. Thieu, Lauren J. Wilkins, & Mariam Aly"
date: "Updated `r Sys.Date()`"
output:
  pdf_document:
    toc: true
  html_document: default
---
